\vskip-0.6in Endogenous Politics and the Design of Trade Institutions

### 2016-04-02 draft.tex
change header for dell laptop; revise abstract

%dell laptop
%\addbibresource{C:/Users/Kristy/Dropbox/Research/xBibs/tradeagreements.bib}
%\addbibresource{C:/Users/Kristy/Documents/Dropbox/Research/xBibs/tradeagreements.bib}

%wallis computer
\addbibresource{C:/Users/wallis/Dropbox/Research/xBibs/tradeagreements.bib}

@@

\begin{quote}
{\small Political pressure is undoubtedly an important influence in the setting of trade policy and the formulation of trade agreements. Most of the literature in this area models the political pressure that governments face as resulting from an exogenous, stochastic process. This paper shows that when political pressure arises endogenously, important results can be overturned and new insights into the motivation for features of the trade agreements we observe and rules of organizations such as the WTO come to light. Developing a model that integrates both exogenous and endogenous political pressure and taking a general approach to the government objective function, I show that governments may want to use tariff caps both to force special interest groups to continue lobbying after a trade agreement is signed and to reduce the magnitude of that lobbying effort. The presence of endogenous politics can also destroy an escape clause's ability to provide flexibility in times of large negative political shocks when lobbies use the flexibility to seek rents. This can explain why use of WTO Safeguards are conditioned on measurable economic indicators as well as why Safeguard levels of protection are not regulated.}
\end{quote}

>>>>

%dell laptop
\addbibresource{C:/Users/Kristy/Dropbox/Research/xBibs/tradeagreements.bib}

%wallis computer
%\addbibresource{C:/Users/wallis/Dropbox/Research/xBibs/tradeagreements.bib}

@@

\begin{quote}
{\small Political pressure is undoubtedly an important influence in the formulation of trade agreements and the institutions that govern them. Much of the literature that speaks to the design of trade policy institutions takes the political pressure that governments face as resulting from an exogenous, stochastic process. This paper shows that when political pressure arises endogenously, important results may be overturned and new insights into the motivation for features of the trade agreements we observe and rules of organizations such as the WTO come to light. Developing a model that integrates both exogenous and endogenous political pressure and taking a general approach to the government objective function, I show that governments may want to use tariff caps both to force special interest groups to continue lobbying after a trade agreement is signed and to reduce the magnitude of that lobbying effort. The presence of endogenous politics can also destroy the ability of an escape clause as traditionally defined in the literature to provide flexibility in times of large negative political shocks when lobbies use the flexibility to seek rents. This can explain why the use of WTO Safeguards are conditioned on measurable economic indicators.}
\end{quote}
